An Experimental Evaluation of Hybrid Vector Search (EA\&B)

### 2025-04-30 VLDB2026/main.tex
modify

	(4)\textbf{ Evaluation of Range Filtering Algorithms.}
	We benchmark 5 range filtering algorithms\textcolor{red}{, 1 library, and 3 databases} on 3 large-scale datasets, using varying query range settings in the experiments. The experimental results demonstrate the performance of these algorithms in terms of index construction efficiency, storage overhead, and query performance. We further analyze performance factors from an algorithmic perspective.

>>>>

	(4)\textbf{ Evaluation of Range Filtering Algorithms.}
	%We benchmark 5 range filtering algorithms\textcolor{red}{, 1 library, and 3 databases} 
	\textcolor{red}{We benchmark 5 algorithms specifically designed for range filtering, along with 5 others applicable to range filtering} on 3 large-scale datasets, using varying query range settings in the experiments. The experimental results demonstrate the performance of these algorithms in terms of index construction efficiency, storage overhead, and query performance. We further analyze performance factors from an algorithmic perspective.
